Brilliant springtime sunlight washed over Island No. 68 as a young girl diligently polished a sword.
\\

It was a massive sword, the length alone practically the same as the girl's height. The luster emitted by its thick blade was undoubtedly that of metal. The blade itself very clearly carried some heft. Regardless of how well it cut, it could probably just bash through one or two plaster walls as easily as a war hammer—its presence was that weighty.

But on a closer look, one could tell that the blade was riddled with what looked like cracks. It didn't appear to be broken, but rather that shards of what seemed to be metal fragments that were once separate had been mashed and patched together. The mere sight of this blade on the verge of falling apart was enough to unsettle a person. Anyone unfamiliar with the sword would surely think that if it was bashed against a wall, both the wall and sword would shatter to pieces.
\\

The girl's little hands were busy washing a cloth with freshly drawn water.

She wrung it out as well as she could, then began to polish the blade.

Not that it was obviously dirty; the blade had simply been untouched for a spell and was a bit dusty as a result. Yet, she paid absolutely no mind to that as she kept her hands moving over the sword, the hint of a smile on her face. \textit{Squeak, squeak, squeak}. The somewhat cute sounds of friction intermingled with the sound of the trees dancing in the spring breeze.

"Lakhesh."

The girl stopped.

She lifted her head and looked behind her. Approaching her was another girl of the same age—around ten years old—looking annoyed.

"What is it?"

"What kind of question is that? It's lunchtime. You never showed up, so I came to get you."

"…Oh!"

The girl, Lakhesh, got to her feet in a fluster. She rushed to continue her interrupted work, though still taking care to be as attentive as she was before. She laid out a white cloth, wrapped the sword loosely in it, and placed it safely hidden from view. Then she wrung out the cleaning cloth and laid it down flat in the sun to dry. She decided to draw some new water later as she poured out what she currently had over the grass.

"I'm sorry. I'll come back soon."

She took the time to bow before turning back to the girl who had come to get her and said, "Thanks for letting me know, Pannibal. Let's go."

"Mm." Judging by the look on her face, Pannibal appeared somewhat befuddled yet slightly curious; she fiddled with her bangs and replied, "Yeah, I suppose we should."

With one last glance toward the sword swathed in the white cloth, they walked off.
\\

"—This is gonna be a weird question, but…," Pannibal started to say on the way back, waving around a stick she'd picked up along the trail.

"What is it?"

"Don't you think Seniorious is a terrible sword?"

"…Huh?"

Lakhesh looked blankly at her.

"I didn't mean to make that sound so mysterious," Pannibal continued. "It's just, remember how only people with the worst fates can wield it? Which means in a way, that sword robbed both Willem and Miss Chtholly of their lives." Pannibal fiddled with the twig in her hand as she spoke. "And if things go the way we think they will, then the next one to be swallowed up by that cycle will be you, Lakhesh."

"Oh…hmm." Lakhesh tilted her head. "I understand why you think that, and I'd be lying if I said I wasn't worried about it at all, but…I'm sure it's actually the other way around."

"The other way around?"

"See, Seniorious hasn't done anything bad. It only ever comes to help people when they're in super-super-bad situations, when they really, really need true power."

Pannibal stopped in place.

Lakhesh stopped as well, then turned around.

"Pannibal?"

"Keep going."

"Oh, okay. Um, I think Seniorious is a kind but strict sword. I think it gives people who can't do anything for themselves anymore, who have run out of options, the tiniest chance to win back something truly precious to them…"

"…Hmm. So that's how you see things."

"Yeah, basically."

Pannibal started walking again. Lakhesh joined her, the two of them walking side by side.

"Miss Chtholly, Mr. Willem, and the people we never knew from five hundred years ago…the Braves who came before us were all saved by Seniorious, bit by bit, in times when they truly had nothing else they could do. We all owe something to it; it's a really fantastic sword."

Pannibal tilted her head, wondering how anyone could owe something to an inanimate object.

But Lakhesh paid her no mind.

"I know that eventually, there'll be a day when I'm the most troubled person in the world, and then Seniorious will have to come and save me. I have to let it know that I'll be counting on it when that happens, so I'm doing my best to get on its good side," she said, pumping her fist in front of her chest.

"Hmm."

"Did that sound dumb?"

"…No." Pannibal smiled lightly, then tossed away the twig she had in her hand. "I was just thinking about how that's a very you thing to say."

"Oh really? So, uh…should I be happy about that?"

"Ha-ha, I knew that was how you'd react, too."

"Ah! Now I get it! You \textit{do} think I'm dumb!"

"Nice to see you're growing up, at least!"

Lakhesh raised her little fist over her head, and Pannibal laughed as she made her escape.

The chase began.

The two girls dashed down the hallway leading to the dining hall in the faerie warehouse.
\\

The wind blew, peeling back just a corner of the cloth wrapped around the Carillon Seniorious. The blade, bathed in the light of the sun overhead, glimmered ever so faintly—almost as though it were shedding tears.
