And then several more years passed.

“C’mon—what else could I say? He really did suck.”

Lillia trudged through the snow as she grumbled about this memory of hers.

“I mean, he got mad when I said so, which means I was right on the mark. And there’s no point in getting mad about something that’s just true. Instead, he should’ve kept his mouth shut, bowed his head low, and then said, ‘You are correct, Princess,’ before going back to his training.”

She was used to traveling alone.

Yet, at the same time, she had completely gotten into the habit of talking to herself.

“…But, I mean, still. I might be used to being alone, but I do think I oughtta stop talking out loud to myself. I’m more or less aware it’s an issue. It’s just plain embarrassing—pathetic, even. If someone heard me, they might think, Gee, Miss Legal Brave’s losing her mystique. I guess that’s the problem here, huh?”

As she kept talking to herself despite what she’d just said, she snapped her head up and looked around.

It was white. Everything was white—so white that it was practically no different from the dark of night.

And it was freezing. This was far beyond simple cold—it was freezing, and it stung.

A famous poet who once visited this land described it as follows: an unending stretch of wilderness, withered trees, and snow that never stopped. The ever-howling wind was the resentment of the dead, the manifestation of their curse to freeze any warm creature to its death. If any place should have been considered the world’s edge, then this had to be it.

As was often the case with poets like these, these words, of course, did not represent the exact truth. The stretch of wilderness did have an end, and the trees that looked withered were happy and healthy plants that were simply adapted to the cold climate, and there were several days throughout the year when it didn’t snow. Pioneering Adventurers later reported that they identified a continent even farther north than this place.

But, well…in reality, if she had to say anything about the wind, she tended to agree with the poet.

It blew high and low, sometimes fiercely but sometimes quietly; it would cling to her in one moment, yet kept its distance in the next—an eddy of sound with such rich expression. When she placed herself in the middle of it, it certainly felt like there was some sort of musician behind her. Whether it be the dead, the gods, the spirits, or the fae—well, it was probably the work of one of those kinds of beings beyond human comprehension—

“Ha-choo!”

Her massive, involuntary sneeze brought her train of thought back to the present.

“…’s cold,” she muttered to herself within her snug winter gear.

As she rubbed the tip of her nose with her finger, she looked down the road again. Beyond her white, hazy vision, on the other side of the flurried dance of the large snowflakes, she could vaguely make out several drab, mud-colored tents standing together.

“There it is.”

She gently shook herself, readjusted what she carried on her back, and began walking again.

\icon

To say that humanity’s history consisted merely of their warring with the monsters would be an outright lie. And yet, there was no mistaking these wars were an important element.

The monsters were all enemies of humans, and they were powerful.

Some attacked with their massive bodies, some trapped their victims using camouflage, while others tricked them with mysterious spells. There were monsters that preyed on humans, monsters that killed for the sake of killing, monsters that toyed with their victims just for fun. Ever since the dawn of civilization, all kinds of monstrous beings had been very close neighbors to humans.

However, humans were not powerful creatures by any means. Their arms were generally scrawny, and their gait was slow. A mere push could prove fatal; burn them, drown them, drop them, starve them, and it would all end in death.

Sure, there were a lot of them. But when it came to pure population numbers, they were a magnitude inferior compared to the likes of the fertile orcs. On top of that, the average citizen had no idea how to fight as a group, so even when they did have a numerical advantage, it did not translate into an increase in strength.

Humans could use weapons and tools of war. But in terms of technological prowess and production capacity, there were other races that were far better. More than half the practical weapons that humanity relied on were just imitations of what the morians had created, rearranged in a way to suit their own needs.

Yet, despite all that, humankind stubbornly thrived to this very day. They warded off danger, opened up the wilderness, and expanded their territory. And along the way, humans created plenty of technology that could allow the weak to fight back against the strong, then refined it and perfected it.

Take, for example, the Adventurers, who were using a unique method to get stronger to better themselves.

Or the soldiers in the military, who protected their homeland with their dauntless will.

Or the scholars in the Imperial Tower of Sages, who passed down ancient wisdom to the present.

Or the puppet soldiers and sorcerers who came with them, who protected tangible things with an intangible bond.

Or perhaps even those warriors chosen by the Church of Exalted Light—the ones called the Steel Saviors, Ancient Myths Reborn in the Present, the Victors of Predetermined Harmony—the most favorite among the favorite of guardians known as Braves…

They were all fighting to protect the human way of life. Rather, they were all fighting for their own selfish reasons, which as a result protected their way of life. And because of that, they had all survived until now.

Lately, there was a certain rumor making its rounds of the continent.

It essentially said that a Visitor had awoken from its slumber, which had lasted since the age of the ancients. The Visitors were a group of superior beings said to have once created everything on the planet. It was said that, in the distant past, all the Visitors left to travel—but there was apparently one outlier. And that one Visitor, of all things, decided it was the enemy of all humanity. It ordered the world’s custodians, the three Poteau, to attack human cultural centers.

Well now, that was a pickle. The continuation of their race was in danger.

The whole story was such a shock, and there was nothing more devastating. But all those who spread the rumor barely registered any sorrow on their faces.

Some all-powerful monsters had appeared—so what? There had always been terrifying creatures like that lurking nearby for as long as anyone could remember. But there were those who would stop them to protect humanity. It was the strong chosen few who would keep them safe.

Humankind would lose nothing. They never had, and they never would.

That was why there was nothing to worry about.

\icon

There was a heavy air within the field tent.

Spread out on the coarsely made war table was a sketched map of the surrounding area. Wood-carved pawns, some painted red and some blue, sat on top of it, indicating where deployed troops were on either side.

There were three men sitting around the table, all wearing similar-looking scowls, staring hard at the table before them.

“…I don’t think we can win like this,” said one of the men, the strategist of the northern defense corps deployed in this area. “We have allowed the enemy’s lines to encroach too far. This has been a long battle, so the soldiers are exhausted, too. At this point, we won’t have enough time to request support from allied troops. Realistically, the only thing we can do is…to ask the Alliance to send reinforcements.”

“But that would besmirch the honor of our forces,” the general, the most important person in the tent, protested bitterly.

After all was said and done, the military was still an organization that wielded violence, and it was common sense that those who were left alone to wield violence unchecked would end up savage and wild. That was why many armies hammered into their troops the importance of having pride.

The northern defense corps, of course, was not an exception. It was incredibly important for them to save face here, and making an attempt to do so was even more precious… Therefore, the general’s response was considered correct for a soldier of the defense corps.

“Then should we perish along with our land to save face?”

But once he was asked that, he had no response.

The last man—the commander, who was not a part of the conversation—kept his arms folded and quietly groaned.

Practically speaking, their battle was progressing horrendously.

The enemy they were up against was a swarm of elves. And the curses emitted by the ancient elves quite literally controlled the land.

The earth that the elves controlled was called murk-wood—purple-streaked poisonous forests.

After hearing that much, just about everyone would interpret this as the elves contaminating the forests. Most were sure that they must give off some kind of venom that corrupted a forest that was there to begin with. How else could they annihilate all the lush green and all the animals that once lived there? Oh, what terrible creatures. What horrifying things.

They thought wrong.

Anyone who had seen them invade with their own eyes knew the truth—the curses the elves used were acts that reconstructed the world.

One theory held that the elves’ ancestors were subordinate spirits born as assistants to the gods when they created this world so long ago. That was why they were often described in documents as the “elder spirits”—because when that happened, it was said that they stole from the gods’ pockets a part of the secret art that could physically change the planet.

This meant there was no need for a forest to exist prior to their invasion.

Even if it was a field or a mountain range or even the wide-open ocean, they would change any place into one of their murk-woods. Earth would appear from nowhere, and thick clusters of warped trees would take root. Unusual insects gathered out of thin air and made their nests. They sat there arrogantly, almost as though they had already been there for millennia.

That was why challenging the murk-woods the elves controlled came with a different sort of danger than the mundane menace of nature. Charging into the deepest parts of these woods was essentially like throwing oneself into the bowels of a ravenous monster.

“—This is entirely different from ordinary human territorial squabbles. A loss here means that this entire land will sink into that swampy miasma. No matter what happens, we cannot lose.”

“But even if we ask for help from Adventurers, would there be any point in the end?”

“What do you mean?”

“Even if there was one elf by itself, it would still be strong. What we are fighting against up here is a swarm of them. Not only that, but it’s the elder kind who wield a curse that’s potent enough to swallow a land as vast as this one. And unlike us, those Adventurer fellows only fight for themselves. Would they leap into the jaws of death for us with nothing but glory to be gained?”

Everyone felt silent.

The commander groaned quietly again.

A slender hand reached beside him and plucked one of the baked sweets that sat on the corner of the war table.

“It goes further than that. There are very few experienced Adventurers who would prove useful in a battle against elves. Could we even expect one of them to conveniently be this far north?”

“Then are you asking us to sit here and wait to die?”

“That is not what I’m saying, but our survival hangs in the balance.”

Fluffy winter gear—someone inside the fluffy winter gear, rather—nibbled on the edge of a cookie while gazing at the war table.

“We have to do something, or nothing will change!”

“That is why I’m telling you that we have no time to be wasting on meaningless measures!”

Neither was going to budge.

Their voices grew louder, their words more violent.

The commander groaned.

Another cookie disappeared.

“…”

“…”

The men all turned to look at the same spot.

The focus of their attention—a fourth person, who seemed to have appeared from nowhere—stopped eating, then looked up at them.

“Who are you?” the strategist asked for all of them.

“Oh, I’m just helping myself to some of your cookies. Gosh, I’m just so hungry after pushing my way through such a cold place. Sooo hungry!”

It was a girl’s voice that spoke, and the stranger pulled back her hood.

Fiery red hair spilled from inside.

What appeared before them was, indeed, a girl.

From just the shape of her face and her physique, she seemed to be in her midteens or a little younger. But her expression, which was oddly somewhat relaxed, wasn’t that of a child. It almost reminded them of an old woman.

“Erm, I’m here to say hello. I’m from the Church of Exalted Light,” the girl said as she rubbed her cheeks, reddened from the cold.

“Excuse me?” The general sounded suspicious. “What, you want to start making arrangements for our funerals? Sorry, but no thanks—you don’t need to worry about us.”

“Well, that’s not exactly it.”

“This is the front line. We’re fighting a desperate battle against formidable enemies. This isn’t the place for children to make some pocket change. Go home, unless you want to lie in the same graves as us.”

The Church had a great variety of stations and staffers. They weren’t all priests who were rewarded with a high salary for simply whittling away their days in the temples performing rites. Some of the clergy who struggled to earn their keep walked across ill-fated battlefields, aggressively selling informal funeral services. That was essentially what the general was talking about.

“Come on, don’t be like that.”

The girl paid him no mind and went back to studying the war table.

“You—”

“Hmm?”

Before the enraged general could say anything, the commander raised his eyebrow slightly.

“Miss, would you mind if I asked about that heavy-looking package you have on your back?”

“It’s a sword,” the girl answered breezily.

“Isn’t that a little big for it to be a normal sword?”

“Yup.”

“Is it Seniorious, the Carillon?”

“Yup.”

The girl nodded lightly.

The general’s expression hardened. Color drained from the strategist’s face, as though in relief. An uncomfortable silence fell over the field tent.

It wasn’t impossible.

There were people in this world who were called Braves. They were not just any people, though. They did not belong to any nation; they fought for the continuation of all humanity and were the ultimate weapon in the endless wars against the monsters. These select few were living legends, all individuals who came with mountains of reasons to explain their impossible strength—be it the ultimate Carillon, an astounding secret art, unparalleled talent, being an ancient guardian, a heroic bloodline, or even a tragic birth.

And Seniorious was the greatest and strongest mystery that modern humans had. It stood at the pinnacle of the countless Carillon, one of five of what were considered the greatest and oldest blades. It had changed hands from chosen one to chosen one, striking down the enemies of humanity on countless battlefields. Its wielder was now the twentieth Legal Brave designated by the Church of Exalted Light—

“Lillia Asplay…?” The general murmured her name.

“Impossible.” The strategist shook his head weakly. “Princess Brave Lillia should have fiery red hair, with beauty like no other. She can’t be this…this smart-mouthed little girl!”

“I’m not responsible for rumors that take on a life of their own…”

“You were a graceful maiden in the portrait of what you might look like one day!”

“I’m not really sure how I should react when you bring up something like that.”

“It was expensive!”

“Uh… My condolences, I guess?”

Another uncomfortable silence fell over them.

The commander, who had refolded his arms, groaned quietly.

“Oh, and here’s proof of my identity,” the girl, Lillia, said as though it had just occurred to her. She pulled out a piece of brass work from her pocket and showed it to the three. It was a type of talisman that the Church issued to their highest-ranking traveling priests and was the single greatest proof that guaranteed who she was.

“…So, Lady Lillia Asplay, what on earth has brought you all the way out here? If you’re here to assist us, then go home.”

“Hmm.” As she swallowed her cookie, she peered down at the map again. “If there are elves here, then does that mean here and here are already forest?”

She pointed at the pawns on the map in turn.

“Yes, that’s exactly it.”

“Don’t humor her, Commander!”

“And that means the elder ones are here and maybe here, too… Man, this sure is a bother.” Lillia scratched at her head as she closed her eyes to think for a moment. “Um, General? I have a request.”

“I won’t give you any troops.”

“No, I want you to move the whole army. The snow is a little deep, so it’s probably going to be a rough trek, but you can move”—she slid a pawn across the map—“like this, right?”

“Don’t be ridiculous!” The general snorted, then looked back down at the map. “…Really, how…ridiculous…”

His expression turned serious. “We would just be moving away from the enemy, no? Even if we withdraw to the town—No, that is also completely out of the question. We’d be going in the wrong direction.”

“Yeah,” Lillia replied with a nod. “Before I arrived, I heard that the battle over here…at Narvant, the City of Weirs, in old Dione territory, was going pretty badly.”

“Oh?”

“They’re mostly up against orcs. It’s not a particularly difficult battle, but the numbers they’re up against are so great that the front line is getting wider, and they’re having trouble maintaining their defenses. It would be a lot easier for you guys to be fighting there instead of going up against elves, right?”

“Well, see… No, that’s not the problem. We cannot surrender here.” Despite how taken aback the general seemed, he still argued.

“Hmm? Do you have something to do here, then?”

“No, what I’m saying is that it is our duty to sweep the elves from this land…”

“Oh yeah, don’t worry about that. I’ll do something about them,” Lillia declared, a hint of vexation in her voice, and she then started rolling her shoulders to loosen them up. “I think it’ll be over in three days or so.”

\icon

Three days passed.

The troops were en route to Narvant, City of Weirs, where they would join up with an allied army when they received a report.

It said that the elven territory—those hated purple forests, which had been spreading without pause until then—had started to wither with vicious speed.

Every soldier reeled from the news.

“It was Lillia Asplay.”

One soldier mentioned her name.

“It was Lillia Asplay! It was the Legal Brave; she did it!”

Their foes had been so powerful that it had seemed impossible for there to be a future where the battle ended. They were exhausted after much arduous fighting. There was a handful who, after watching their friends melt in acid and be eaten by elves, had lost all hope, wondering if they would be next.

A single girl who had leaped out from nowhere had put an end to that battle.

“—I don’t like it,” the general spat, his face twisted as though he’d swallowed something bitter. “We fruitlessly risked our lives for child’s play that a little girl took care of in her spare time. What was our fight—no, what were we for?”

As a person of his standing, he did have basic knowledge as to what kind of people the Braves were. Actually, he had done a little more research than that. According to what he knew, a Brave’s strength was supposedly supported by persuasive power. The more dramatic a past they shouldered or the greater their despair, the more they were suited to being a strong Brave.

And so what sort of person was that girl—the twentieth Legal Brave, Lillia Asplay?

She had lost her beloved family and home, and she stewed in anger and sadness. And all those emotions pushed the young princess into a life of battle.

The strength given only to those who shouldered sadness, power allowed only for those who went through unspeakable pain, strength admitted only to those who clawed their way out from a pit of despair, power that fed on anger, strength that could only rest on shoulders that overcame their hate—all that was stuffed into her tiny body, and what was born as a result was a Legal Brave, a weapon wielded by the Church of Exalted Light.

“—Yeah, I don’t like this.”

He checked to make sure no one was around before he pulled a pouch from his pocket. He took out a small, folded piece of paper and unfolded it. Drawn on it was a beautiful girl with burning red hair whose smile felt somewhat maternal.

He wanted to rip it to shreds.

He hesitated.

He neatly refolded it and placed it in his pouch, then returned the pouch to his pocket.

“Hmph.”

Then, in a gesture of defiance, he looked up to the sky.

There was no snow falling here. He saw a long-tailed bird cut across the blue sky.